Objectives and Ideas

### 2020-09-29 README.Rmd
updating readme

Repository for research projects on LIME

Link to csafe server: https://isu-csafe.stat.iastate.edu/rstudio/

## Ideas

**LIME diagnostics**

- turn repetitive code into functions
- try out different weights
- change distance matrix in seriation to be 5-# of variables shared between two rows
- try using distance matrix computed on the feature value with seriation
- add in feature selection methods to LIME input options
- think of a way to compute consistency across top two features
- Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
- he also suggested looking into SMOTE for dealing the imbalance in the classes with sampling
- compare the simple models based on different number of bins using an F-test
- look into computing a diversity or consistency measure for the sensitivity analysis
- include a penalty for the number of parameters when choosing bins
- look at the AUC after binning
- compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
- try visualizing the features from the test data using dimension reduction and
coloring them by variables suggested to be important by lime

**Explainer Models**

- read through papers giving an overview of the current explanation methods
- look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
- look more into Molnar and his adviser Bernd
- look into [MAPLE](https://blog.ml.cmu.edu/2019/07/13/towards-interpretable-tree-ensembles/)

**Understanding LIME**

- edit details in understanding LIME journal
- look at the RF in the local region lime is considering to see if it agrees with the lime explanations
- try fitting LASSO logistic model and leave one out approach (for multicollinarity)
- assess lime results on logistic regression models
- try retriculate to apply python version of lime
- look into literature on binning methods
- think about why R^2 would be better for some binning methods
- read new paper on Anchor

**Possible Improvements to LIME**

- determine the best number of bins to use for each variable
- try out subsampling idea

**Simulation with RF**

- think about how to implement a simulation with a random forest
- look back at 601 notes from Kaiser for model assessment
- look at Hadley's 'removing the blindfold' for ideas
- read book Dr. Dixon lent me on sensitivity analyses

**Random Forests Confidence Intervals**

- look into papers by Giles Hooker and Lucas Mentch
- Dr. Nettleton paper

**Random Forest Interpretations**

- read https://www.r-bloggers.com/explaining-predictions-random-forest-post-hoc-analysis-randomforestexplainer-package/

>>>>

Repository for research journals for my research projects related to LIME. See below for descriptions of the contents of this repository. For easy viewing of the journals, use these links:

0. [Objectives and Ideas]()
1. [Information on Hamby Data and Models]()
2. [Understanding LIME]()
3. [Applying LIME to Hamby Data]()
4. [Assessing LIME on Hamby Data]()
5. [Applying and Assessing LIME on Iris Data]()
6. [Notes on Readings]()
7. [Computational Issues]()
8. [LIME Applied to Logistic Regression]()
9. [Identifying `rtrees` Training Data]()
10. [LIME Variability Across Hamby Data and Models]()

### 2020-09-29 journals/00-objectives_and_ideas/00-objectives_and_ideas.Rmd
updating readme

@@

# Ideas to Try

- Could try fitting a regression with interactions and see if LIME does a good job of explaining a model that is already interpretable.
- Run a simulation to understand if LIME is working
    - could implement a couple of local linear dependencies
    - piece this together
    - could include interactions in the model
    - does lime find the local models?
- Maybe we could come up with a test to compare between global and local explanations (but how would we do this?)

>>>>

### Ideas

**LIME diagnostics**

- turn repetitive code into functions
- try out different weights
- change distance matrix in seriation to be 5-# of variables shared between two rows
- try using distance matrix computed on the feature value with seriation
- add in feature selection methods to LIME input options
- think of a way to compute consistency across top two features
- Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
- he also suggested looking into SMOTE for dealing the imbalance in the classes with sampling
- compare the simple models based on different number of bins using an F-test
- look into computing a diversity or consistency measure for the sensitivity analysis
- include a penalty for the number of parameters when choosing bins
- look at the AUC after binning
- compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
- try visualizing the features from the test data using dimension reduction and
coloring them by variables suggested to be important by lime
- Could try fitting a regression with interactions and see if LIME does a good job of explaining a model that is already interpretable.
- Maybe we could come up with a test to compare between global and local explanations (but how would we do this?)

**Explainer Models**

- read through papers giving an overview of the current explanation methods
- look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
- look more into Molnar and his adviser Bernd
- look into [MAPLE](https://blog.ml.cmu.edu/2019/07/13/towards-interpretable-tree-ensembles/)

**Understanding LIME**

- Run a simulation to understand if LIME is working
    - could implement a couple of local linear dependencies
    - piece this together
    - could include interactions in the model
    - does lime find the local models?
- edit details in understanding LIME journal
- look at the RF in the local region lime is considering to see if it agrees with the lime explanations
- try fitting LASSO logistic model and leave one out approach (for multicollinarity)
- assess lime results on logistic regression models
- try reticulate R package to apply python version of lime
- look into literature on binning methods
- think about why R^2 would be better for some binning methods
- read new paper on Anchor

**Possible Improvements to LIME**

- determine the best number of bins to use for each variable
- try out subsampling idea

**Simulation with RF**

- think about how to implement a simulation with a random forest
- look back at 601 notes from Kaiser for model assessment
- look at Hadley's 'removing the blindfold' for ideas
- read book Dr. Dixon lent me on sensitivity analyses

**Random Forests Confidence Intervals**

- look into papers by Giles Hooker and Lucas Mentch
- Dr. Nettleton paper

**Random Forest Interpretations**

- read https://www.r-bloggers.com/explaining-predictions-random-forest-post-hoc-analysis-randomforestexplainer-package/

@@
